Marlowe: financial contracts on blockchain\thanks{This work is part of the Cardano project and is supported by IOHK,~\url{https://iohk.io}}

### 2018-05-19 tex/paper.tex
Move acknowledgement and fix layout

%
%
% Title portion. Note the short title for running heads
\title {Marlowe: financial contracts on blockchain}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Pablo Lamela Seijas\orcidID{0000-0002-1730-1219}\\
\and Simon Thompson\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas and S. Thompson}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Computing, University of Kent, Canterbury, UK}
\email{\{pl292,s.j.thompson\}@kent.ac.uk}

@@

This paper explores the design of a domain specific language, Marlowe,\footnote{Named after Christopher 
Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury,  \url{en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{Marlowe is available 
from \url{https://github.com/input-output-hk/scdsl}} targetted at the execution of financial contracts in the style of 
Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains. This work is a part of the Cardano project, and is 
supported by IOHK,~\url{https://iohk.io}.

@@

\smallskip
\noindent
\haskellinline{Null} is the null contract; it will always be quiescent:

@@

\smallskip
\noindent
\haskellinline{CommitCash ident person val start_timeout end_timeout con1 con2}  For this contract to make 
progress,\begin{itemize}
\item either, before the timeout \haskellinline{start_timeout}, the user \haskellinline{person} makes a cash commitment of 
value 
\haskellinline{val} and timeout \haskellinline{end_timeout}  with the identifier \haskellinline{ident}, 
\item
or the timeout \haskellinline{start_timeout} is exceed:
\end{itemize}

@@

\medskip
\noindent
\haskellinline{RedeemCC ident con} (\haskellinline{CC} stands for cash commitment.) For this contract to make 
progress, the creator of the cash commitment with identifier \haskellinline{ident} is allowed to redeem the unspent 
funds in that commitment; the contract then continues as \haskellinline{con}, and the action 
\haskellinline{CommitRedeemed} is produced.

@@

\medskip
\noindent
\haskellinline{Pay idpay from to val expi con} makes it possible, assuming that sufficient funds are available, for 
\haskellinline{to} to claim a payment with id \haskellinline{idpay} of \haskellinline{val} from \haskellinline{from} 
before the timeout \haskellinline{expi}. The contract continues as \haskellinline{con}.

@@

\medskip
\noindent
\haskellinline{Both con1 con2} enforces the behaviour of both contracts \haskellinline{con1} and \haskellinline{con2}. 
\begin{haskellcode}
step comms st (Both con1 con2) os =
    (st2, result, ac1 ++ ac2)
    where
        result | res1 == Null = res2
               | res2 == Null = res1
               | otherwise = Both res1 res2
        (st1,res1,ac1) = step comms st con1 os
        (st2,res2,ac2) = step comms st1 con2 os
\end{haskellcode}
Because the model is stateful and produces output actions, to make a step, it is necessary to execute a single step of 
each of  the contracts \haskellinline{con1} and \haskellinline{con2} in sequence: first \haskellinline{con1} then 
\haskellinline{con2}.

\medskip
\noindent
\haskellinline{Choice obs conT conF} behaves as either \haskellinline{conT} or \haskellinline{conF} depending on the 
(Boolean) result of \haskellinline{obs} at the time that the observation is made, \haskellinline{conT} if it is 
\haskellinline{True} and \haskellinline{conF} if \haskellinline{False}.

@@

\medskip
\noindent
\haskellinline{When obs expi con con2} This contract will not progress until \haskellinline{obs} is 
\haskellinline{True} or until the current block number is greater than or equal to the one specified by timeout 
\haskellinline{expi}. In case the timeout applies, the contract will continue as \haskellinline{con2}, if the timeout 
does not apply and \haskellinline{obs} is \haskellinline{True}, then the contract continues as \haskellinline{con}. 
Otherwise the contract is quiescent.

\begin{haskellcode}
step _ st (When obs expi con con2) os
  | expired (blockNumber os) expi = (st,con2,[])
  | interpretObs st obs os = (st,con,[])
  | otherwise = (st, When obs expi con con2, [])
  \end{haskellcode}
We look next at an example of Marlowe in action.

>>>>

%
%
% Title portion. Note the short title for running heads
\title {Marlowe: financial contracts on blockchain\thanks{This work is part of the Cardano project 
and is supported by IOHK,~\url{https://iohk.io}}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Pablo Lamela Seijas\orcidID{0000-0002-1730-1219}\\
\and Simon Thompson\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas and S. Thompson}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Computing, University of Kent, Canterbury, UK}
\email{\{pl292,s.j.thompson\}@kent.ac.uk}

@@

This paper explores the design of a domain specific language, Marlowe,\footnote{Named after Christopher 
Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury,  \url{en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{Marlowe is available 
from \url{https://github.com/input-output-hk/scdsl}} targetted at the execution of financial contracts in the style of 
Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains.

@@

\begin{itemize}
\item \haskellinline{Null} is the null contract; it will always be quiescent:

@@

\medskip
\noindent
\item \haskellinline{CommitCash ident person val start_timeout end_timeout con1 con2}  For this contract to make 
progress,\begin{itemize}
\item either, before the timeout \haskellinline{start_timeout}, the user \haskellinline{person} makes a cash commitment of 
value 
\haskellinline{val} and timeout \haskellinline{end_timeout}  with the identifier \haskellinline{ident}, 
\item
or the timeout \haskellinline{start_timeout} is exceed:
\end{itemize}

@@

\medskip
\noindent
\item \haskellinline{RedeemCC ident con} (\haskellinline{CC} stands for cash commitment.) For this contract to make 
progress, the creator of the cash commitment with identifier \haskellinline{ident} is allowed to redeem the unspent 
funds in that commitment; the contract then continues as \haskellinline{con}, and the action 
\haskellinline{CommitRedeemed} is produced.

@@

\medskip
\noindent
\item \haskellinline{Pay idpay from to val expi con} makes it possible, assuming that sufficient funds are available, 
for \haskellinline{to} to claim a payment with id \haskellinline{idpay} of \haskellinline{val} from 
\haskellinline{from} before the timeout \haskellinline{expi}. The contract continues as \haskellinline{con}.

@@

\medskip
\noindent
\item \haskellinline{Both con1 con2} enforces the behaviour of both contracts \haskellinline{con1} and 
\haskellinline{con2}. 
\begin{haskellcode}
step comms st (Both con1 con2) os =
    (st2, result, ac1 ++ ac2)
    where
        result | res1 == Null = res2
               | res2 == Null = res1
               | otherwise = Both res1 res2
        (st1,res1,ac1) = step comms st con1 os
        (st2,res2,ac2) = step comms st1 con2 os
\end{haskellcode}
Because the model is stateful and produces output actions, to make a step, it is necessary to execute a single step of 
each of  the contracts \haskellinline{con1} and \haskellinline{con2} in sequence: first \haskellinline{con1} then 
\haskellinline{con2}.

\medskip
\noindent
\item \haskellinline{Choice obs conT conF} behaves as either \haskellinline{conT} or \haskellinline{conF} depending on 
the 
(Boolean) result of \haskellinline{obs} at the time that the observation is made, \haskellinline{conT} if it is 
\haskellinline{True} and \haskellinline{conF} if \haskellinline{False}.

@@

\medskip
\noindent
\item \haskellinline{When obs expi con con2} This contract will not progress until \haskellinline{obs} is 
\haskellinline{True} or until the current block number is greater than or equal to the one specified by timeout 
\haskellinline{expi}. In case the timeout applies, the contract will continue as \haskellinline{con2}, if the timeout 
does not apply and \haskellinline{obs} is \haskellinline{True}, then the contract continues as \haskellinline{con}. 
Otherwise the contract is quiescent.

\begin{haskellcode}
step _ st (When obs expi con con2) os
  | expired (blockNumber os) expi = (st,con2,[])
  | interpretObs st obs os = (st,con,[])
  | otherwise = (st, When obs expi con con2, [])
  \end{haskellcode}
\end{itemize}
We look next at an example of Marlowe in action.
